Highlighting Disputed Claims on the Web

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
Changes suggested by Beth

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that frequently appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``Eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are {\it paraphrases} of the same claim. For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim. A snippet is a continuous region of text on a web page. A snippet is considered to {\it entail} a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the English have as many words for rain as the Eskimos have for snow'' {\it entails} ``Eskimos have many words for snow'', even though this claim is never stated explicitly.

@@

One weakness of the automatic import approach is that the claims on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''. In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{pictures/article_choose_claim.png}
	\caption{Choose how to connect an article with a claim.}
	\label{article_choose}
	\end{center}
\end{figure}

@@

Unfortunately, as Pew Research discovered~\cite{PewResearch2008} when looking at TV news, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. Similarly, Manjou~\cite{Manjou2008} reports that people tend to measure the credibility of a source based on how well it fits with what they already believe to be true.  As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.5cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.

>>>>

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that frequently appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``Eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim. For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to entail a claim. A snippet is a continuous region of text on a web page. A snippet is considered to entail a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the English have as many words for rain as the Eskimos have for snow'' entails ``Eskimos have many words for snow'', even though this claim is never stated explicitly.

@@

One weakness of the automatic import approach is that the claims on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: matching happens on the client, using a database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/paraphrases2.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5.5cm]{pictures/article_choose_claim.png}
	\caption{Choose how to connect an article with a claim.}
	\label{article_choose}
	\end{center}
\end{figure}

@@

Unfortunately, as Pew Research discovered~\cite{PewResearch2008} when looking at TV news, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view. Similarly, Manjou~\cite{Manjou2008} reports that people tend to measure the credibility of a source based on how well it fits with what they already believe to be true.  As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked one claim as opposing another  when they were referring to similar incidents that occurred at different times.
